Collaborative Visual Analysis with RCloud

### 2015-07-13 interviews.tex
remove reference to iotools/hmr
not properly anonymized

To evaluate the effectiveness of RCloud, we interviewed 13 current or
recent users of RCloud. 9 are data analysts, and 4 build tools for data
analysts and business needs. Users felt that sharing works well, but the notebook
interface slows down exploration, and the browsing interface is not scaling well.
%gw (trying to be specific)

@@

Eric develops packages for analysts, and uses RCloud ``for sharing code with
other people, and for doing tutorials for {\em iotools} or {\em hmr}'', his packages.
``I want people to see how the package works, so I clearly want them
to see the code... I write it just like I would write GitHub
Markdown, where you have little code snippets and text, but RCloud lets me
actually run the snippets [and display the results].'' He also uses RCloud for
describing and debugging data sources.

>>>>

To evaluate the effectiveness of RCloud, we informally interviewed 13 current or
recent users of RCloud. 9 are data analysts, and 4 build tools for data
analysts and business needs. Users felt that sharing works well, but the notebook
interface slows down exploration, and the browsing interface is not scaling well.
%gw (trying to be specific)

@@

Eric develops packages for analysts, and uses RCloud ``for sharing code with
other people, and for doing tutorials for'' the packages he develops.
``I want people to see how the package works, so I clearly want them
to see the code... I write it just like I would write GitHub
Markdown, where you have little code snippets and text, but RCloud lets me
actually run the snippets [and display the results].'' He also uses RCloud for
describing and debugging data sources.
